---
title: "Airbnb Project"
subtitle: "Charlene BRUNO, Loic CHANG, Pierre PHILBERT, SORY Anas"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown
Explication objectifs 
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word do cuments. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Explication du preprocess


## Lecture de la donnée 

## Explication de l'architechrure de l'app 

## Lecture de la donnée 

## Explication Tab 1 ( screen )

## Explication Tab 2 ( sreen )

## Distribuée avec rshinny 

## Bilan de l'analyse 




## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

